``FISTA'' in Banach spaces with adaptive discretisations

### 2021-09-29 response.tex

We would like to thank both the reviewers for their time and feedback. All changes are marked in the supplementary pdf and a detailed response to each reviewer is given below.

\section{Detailed response to first reviewer}

\begin{enumerate}
	\item \review{The authors base much of the analysis on the objective function and its convergence properties \ldots it would be interesting to know how the solutions $w_n$ converge for the various versions of FISTA.}

	We thank the reviewer for their suggestion but it seems quite challenging to make a general statement. As in your comment, if one has coercivity then the convergence is clear. More generally, FISTA is known to converge weakly in the Hilbert-space setting. This is also likely to hold with our algorithm when the minimiser is in $\F H$, but we have not verified this special case. A key component of the proof is the bound $\lVert u_n-u_{n-1}\rVert = o(n^{-1})$, in general we do not even expect this quantity to be bounded. It's not clear whether we can leverage the Hilbert-norm structures of FISTA to gain any convergence in the Banach space. In the LASSO case we know that the sequence is bounded in the L1 norm, so a subsequence must converge weakly, however, it's still unclear how to upgrade from convergence of a sub-sequence to full convergence.

@@

	\item \review{page 12 and elsewhere: $\partial E$ is usually referred to as the subdifferential. I suppose this depends on the literature source you use.}

	As suggested, we have switched to using the term `subdifferential' throughout the document.

	\item \review{My only ``disappointment'' with the paper is that the theory is illustrated with LASSO. As a result, $E$ has a rather favorable structure. There are many examples, e.g., in robust statistics, where it would be more appropriate to use the $\ell^1$ norm instead of the $\ell^2$ norm for misfit. Since the favorable properties of the squared $\ell^2$-norm are often used in the derivations (bounds, constants, etc. in Section 6), I wonder how hard it would be to do the same for other relevant examples.}

	You are right, we can also consider alternative misfits. We have replaced the wavelet example in Section 7.2 with a (Huber-smoothed) robust $\ell^1$ penalty as we only explicitly required the gradient and Lipschitz constant for computations. This also led to a number of small updates to the analysis in Section 6 to generalise to a non-quadratic misfit.

@@

	\item \review{On page 18, the authors state: ``Suppose that the numerical aim is to find a function $u_n$ with $E_0(u_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms.''}

	\review{This is used to argue that the adaptive schemes are better as they require smaller problems, less memory and less time to get to this point. However, it would appear that Figure 2 indicates that if a sufficiently accurate solution were desired, instead of a point with $E_0(u_n)\leq 0.1$, then we would still need orders of magnitude of 10 more iterations to get to the same accuracy as the nonadaptive schemes.}

	We have updated Figure 2 to show both discrete and continuous gaps to improve clarity. The point of Figure 2 (and 3) is to demonstrate the accuracy of our theoretical rate predictions. While the initial rate of convergence is faster for the nonadaptive schemes, Figure 4 confirms that this does not translate to a large practical improvement.
\end{enumerate}

\section{Detailed response to second reviewer}
We are very sorry that you found our manuscript so difficult to read. You were right, the former foundations were not rigorous enough. We have rewritten these sections in line with your suggestion of removing the emphasis on the Banach space. The analysis of the algorithm in the first half of the manuscript is now performed without mention of a Banach space. Consequently, we also realised that the orthogonal projection was not required either, we now allow $U^n$ to be subsets of $\F H$ rather than subspaces. The Banach space setting is reserved for examples discussed in Sections 5 to 7.

### 2021-09-30 paper.tex
typo

	\paragraph{Step 2: Quantifying the scaling properties}
	\begin{adaptiveStep}\label{step: step 2 smoothness}
		To show that the extra terms in \eqref{eq: mini FISTA convergence} are small, we need to quantify the approximation properties of $\spcf0^n$. To do so, we construct a secondary sequence $n_0 < n_1 < \ldots$ and constants $\vars3_{\Varf0},\vars3_{\op{E}}\geq1$ such that for each $k\in\F N$
		\begin{equation}
			n\leq n_k \implies \norm{\varf2_n} \lesssim \vars3_{\Varf0}^k, \qquad n\geq n_k \implies \op{E}_0(\varf2_n) \lesssim \vars3_{\op{E}}^{-k}.
		\end{equation}
		The choice of exponential scaling is very natural if we consider the $\spcf0^n$ to be the subspace of functions discretised on a uniform mesh. If that mesh sequentially refined, then the resolution of the mesh will be of order $h^k$ after $k$ refinements and for some $h<1$. The integer $n_k$ should then be the time when the mesh has refined $k$ times.\edit{}{ Another canonical choice would be $\spcf0^n=\{\varf0\in\F H\st \norm{\varf0}\leq \vars3_{\Varf0}^k\}$. The exponential scaling is less natural, but leads to better convergence guarantees.}

		\edit{The value of $\vars3_{\Varf0}$ is dictated by the smoothness of the norm of $\spcf0$ with respect to that of $\F H$. If $\norm{\varf0^*}<\infty$, then the value is $\vars3_{\Varf0}=1$, otherwise there is some damage to the rate of convergence generated by this factor. On the other hand, the value of $\vars3_{\op{E}}$ is dictated by the smoothness of $\op{E}$ at the point $\varf0^*$.}{Suppose $\F H$ is contained in a Banach space $(\spcf0,\Norm\cdot)$ such that $\Norm{\varf2_n}\lesssim 1$, then $\vars3_{\Varf0}$ reflects the smoothness between the two norms. If $\vars3_{\Varf0}>1$, then we cannot guarantee the original $n^{-2}$ rate of convergence. On the other hand, the value of $\vars3_{\op{E}}$ is dictated by the smoothness of $\op{E}$ (measured in $\Norm\cdot$) near minimisers.} %
		If an efficient basis is used, then $\vars3_{\op{E}}$ is large. The trade-off between $\vars3_{\op{E}}$ and $\vars3_{\Varf0}$ dictates the final convergence rate of the algorithm.
	\end{adaptiveStep}

@@

	\section{\edit{Lasso}{L1 penalised} minimisation}\label{sec: Lasso definition}
	We now focus on the specific example of \edit{Lasso}{L1 penalised optimisation} which will be used for numerical results in \edit{Sectoin}{Section}~\ref{sec: numerics}. We consider three forms \edit{of Lasso}{} which will be referred to as the continuous, countable, and discrete \edit{Lasso}{problem} depending on whether the space $\spcf0$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or finite dimensional respectively. In each case, the energy can be written as 
	\begin{equation}\label{eq: Lasso energy}
		\op{E}(\varf0) = \edit{\tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf0-\data)} + \mu\Norm{\varf0}
	\end{equation}
	for some $\A\colon \spcf0\to\R^m$ and $\mu>0$, where $\Norm\cdot=\norm\cdot_1$. \edit{}{We assume $\op{f}\in C^1(\R^m)$ is convex with $\nabla\op{f}$ 1-Lipschitz and locally bounded, and in the continuous-space case, we require $\A^*\colon\R^m\to C(\Domain)$. }Let $\varf0^*\in\argmin_{\varf0\in\spcf0}\op{E}(\varf0)$.

@@

	Application of Theorem~\ref{thm: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ although \edit{although}{} $\Norm\cdot$ is too strong a metric and results in $\vars3_{\op{E}}=2^0$. This can be seen because for any $\varf0\in L^1(\Domain)$ and Dirac mass $\delta$ supported in $(0,1)^d$, 
	\begin{equation}
		\Norm{\varf0-\delta} = \sup_{\vard0\in C(\Domain), \norm{\vard0}_{L^\infty}\leq 1} \IP{\vard0}{\varf0-\delta} = \Norm{\varf0}+\Norm{\delta} \geq 1 = \meshsize^0.
	\end{equation}
	To improve our estimate of $\vars3_{\op{E}}$ requires additional assumptions on $\A$. \edit{}{Note that the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\spcf0}^k$ onto piecewise-constant functions is $\Norm\cdot$-diminishing. Therefore }
	for any $\varf0\in\F H$, $\varf2\coloneqq \tilde{\tens{\Pi}}_k\varf0\in\tilde{\spcf0}^k$ we have
	\begin{align}
		\op{E}(\varf2)-\op{E}(\varf0) &= \edit{\tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf2-\data)-\op{f}(\A\varf0-\data)} + \mu\left(\Norm{\varf2}-\Norm{\varf0}\right)
		\\&= \ip{\nabla \op{f}(\A\varf2-\data)}{\A(\varf2-\varf0)}
		\\&\lesssim_{\edit{}{\op{E}(\varf2)}} \edit{\max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0-\data}_{\ell^2})}{}\norm{\A(\varf2-\varf0)}_{\ell^2}.
	\end{align}
	\edit{Choosing $\varf2 = \tilde{\tens{\Pi}}_k\varf0^*$ for any bounded linear extension to the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\spcf0\to\tilde{\spcf0}^k$ gives
	\\\centerline{$\displaystyle\op{E}(\varf2)-\op{E}(\varf0^*) \lesssim \norm{\A(\tilde{\tens{\Pi}}_k\varf0^*-\varf0^*)}_{\ell^2} \leq \norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty}\Norm{\varf0^*}.$}
	Expanding the operator norm further,
	\\\centerline{$\displaystyle
		\norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain} \frac{|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|}{\norm{\vvarx3}_{\ell^2}} \leq \sup_{\vvarx3\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}}{\norm{\vvarx3}_{\ell^2}} 
		= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}$}
	}{This norm further simplifies with
	\begin{multline}
		\norm{\A(\tilde{\tens{\Pi}}_k\varf0-\varf0)}_{\ell^2}
		 = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vvarx3}{\varf0}
		\leq \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|\:\norm{\vvarx3}_{\ell^2}^{-1}\Norm{\varf0}
		\\\leq \sup_{\vvarx3\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}\: \norm{\vvarx3}_{\ell^2}^{-1} \Norm{\varf0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\varf0}
	\end{multline}}
	where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$. \edit{}{Sub-levelsets of $\op{E}$ are compact in $L^1(\Domain)$, therefore there exists a weak$^*$-converging minimising sequence $\varf0^*_j\in\F H$ such that $\varf0^*_j\rightharpoonup\varf0^*$ and $\lim_{j\to\infty}\op{E}(\varf0^*_j)=\op{E}(\varf0^*)$. 
		Combining these estimates gives 
		\begin{equation}
			\inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0^*) = \lim_{j\to\infty} \inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0_j^*) \leq \lim_{j\to\infty} \op{E}(\tilde{\tens{\Pi}}_k\varf0_j^*)-\op{E}(\varf0_j^*) \lesssim 2^{-k}|\A^*|_{\ell^2\to C^1}\Norm{\varf0^*}.
		\end{equation}}

@@

	Heuristically, we will use strong convexity of $\op{E}^*$ and smoothness of $\A^*$ to quantify the statement:
	$$ \text{if}\quad \op{E}(\varf0_n) + \op{E}^*(\vars2_0 \vvard0_n) \approx 0 \quad \text{then}\quad \left\{\vvarx0\st \mu - |[\A^*\vvard0_n](\vvarx0)|\ll 1\right\} \subset\{\vvarx0 \st \varf0^*(\vvarx0)=0\}.$$
	\edit{First we use the strong convexity of $\op{E}^*$}{Recall that $\nabla\op{f}$ is 1-Lipschitz if and only if $\op{f}^*$ is 1-strongly convex. \todo{Is there a reference for this? I can't find it in Rockafellar.} Therefore}, if $\vars2_0\vvard0_n$ and $\vvard0^*$ are both dual-feasible, then
	\begin{equation}
		\tfrac12\norm{\vars2_0\vvard0_n-\vvard0^*}_{\ell^2}^2 \leq \op{E}^*(\vars2_0\vvard0_n) - \op{E}^*(\vvard0^*) = \op{E}^*(\vars2_0\vvard0_n) + \op{E}(\varf0^*) \leq \op{E}^*(\vars2_0\vvard0_n) + \op{E}(\varf0_n),
	\end{equation}
	which gives an easily computable bound on $\norm{\vars2_0\vvard0_n-\vvard0^*}_{\ell^2}$. Now we estimate $\A^*\vvard0_n$ on the support of $\varf0^*$:
	\begin{align}
		\min_{\vvarx0\in\supp(\varf0^*)} |[\tens{\Pi}_n\A^*\vvard0_n](\vvarx0)| &\geq \min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vvard0_n](\vvarx0)|
		\\&= \vars2_0^{-1}\min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vars2_0 \vvard0_n](\vvarx0)|
		\\&\geq \vars2_0^{-1}\min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vvard0^*](\vvarx0)| - |[\A^*\vars2_0 \vvard0_n-\A^*\vvard0^*](\vvarx0)|
		\\&= \vars2_0^{-1}\min_{\vvarx0\in\supp(\varf0^*)} \mu - |[\A^*\vars2_0 \vvard0_n-\A^*\vvard0^*](\vvarx0)|
		\\&\geq \vars2_0^{-1}\left(\mu - |\A^*|_{\ell^2\to L^\infty}\norm{\vars2_0 \vvard0_n-\vvard0^*}_{\ell^2}\right).
	\end{align}
	Therefore,
	\begin{equation}
		|[\tens{\Pi}_n\A^*\vars2_0\vvard0_n](\vvarx0)|< \mu - \sqrt{2(\op{E}(\varf0_n)+\op{E}^*(\vars2_0\vvard0_n))}|\A^*|_{\ell^2\to L^\infty} \qquad \implies \qquad \varf0^*(\vvarx0)= 0.\label{eq: support equation}
	\end{equation}
	This equation is valid when $\vvarx0$ is either a continuous or countable index, the only distinction is to switch to $\ell^\infty$ in the norm of $\A^*$. To make the equivalent statement on the discretised problem, simply replace $\vars2_0$ with $\vars2$ and $\A^*$ with $\tens{\Pi}_n\A^*$. There are two short observations on this formula:
	\begin{itemize}
		\item The convergence guarantee from Theorem~\ref{thm: exponential FISTA convergence} is for the quantity $\op{E}(\varf0_n)-\op{E}(\varf0^*)$, the more relevant quantity here is $\op{E}^*(\vars2_0\vvard0_n)+\op{E}(\varf0^*)$ for which there is no proven rate of convergence.
		\item In Section~\ref{sec: continuous lasso rate}, $|\A^*|_{\ell^2\to C^1}<\infty$ was required to compute a rate of convergence for $\op{E}(\varf0_n)$, but only $|\A^*|_{\ell^2\to L^\infty}<\infty$ is needed to estimate the support.
	\end{itemize}

@@

	\subsection{1D continuous Lasso}\label{sec: 1D Lasso examples}
	In this example we choose $\spcf0=\C M([0,1])$\edit{}{, $\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$} and $\A\colon \spcf0\to \R^{30}$ with either random Fourier kernels:
	\begin{equation}
		(\A\varf0)_j = \int_0^1\cos(\vars3_j\varx0)\varf0(\varx0), \qquad \vars3_j\sim \op{Uniform}[-100,100],\ j=1,2,\ldots,30,\ \mu =0.02, 
	\end{equation}
	or Gaussian kernels on a regular grid:
	\begin{equation}
		(\A\varf0)_j = (2\pi\sigma^2)^{-\frac12}\int_0^1\exp\left(-\frac{(\varx0-(j-1)\Delta)^2}{2\sigma^2}\right)\varf0(\varx0), \quad \sigma=0.12,\ \Delta = \tfrac1{29},\ j=1,2,\ldots,30,\ \mu=0.06.
	\end{equation}

	Several variants of FISTA are compared for these examples but the key alternative shown here is the CBP discretisation.\edit{There are many methods designed to minimise the continuous Lasso energy in \eqref{eq: Lasso energy}}{For this choice of $\op{f}$, we call \eqref{eq: Lasso energy} the continuous Lasso problem, for which there are many numerical methods} (c.f. \cite{Bredies2013,Castro2016,Boyd2017,Catala2019}) however, most \edit{}{require} the solution of a non-convex problem. We have focused on CBP because it approximates $\varf0^*$ through a convex discrete optimisation problem which is asymptotically exact in the limit $\meshsize\to0$. It can also be optimised with FISTA which allows for direct comparison with the uniform and adaptive mesh approaches. The idea is that for a fixed mesh, the kernels of $\A$ are expanded to first order on each pixel and a particular first order basis is also chosen \cite{Ekanadham2011,Duval2017b}. If $\varf0^*$ has only one Dirac spike in each pixel, then the zeroth order information should correspond to the mass of the spike and additional first order information should determine the location.

@@

	\begin{figure}\centering
		\includegraphics[width=.84\textwidth]{lasso_ndofs_convergence}
		\caption{Rates of continuous/discrete gap convergence for different Lasso algorithms with 128, 256, or 512 pixels. The `adaptive' method uses the proposed algorithm. Both `fixed' and `CBP' use standard FISTA with a uniform discretisation.}\label{fig: convergence with ndofs}

>>>>

	\paragraph{Step 2: Quantifying the scaling properties}
	\begin{adaptiveStep}\label{step: step 2 smoothness}
		To show that the extra terms in \eqref{eq: mini FISTA convergence} are small, we need to quantify the approximation properties of $\spcf0^n$. \edit{}{The idea is that $\spcf0^n$ are locally compact, so that minimisers are achieved, but `growing' so that $\min_{\varf0\in\spcf0^n}\op{E}(\varf0) \to \inf_{\varf0\in\F H}\op{E}(\varf0)$. A canonical example might be $\spcf0^n=\{\varf0\in\F H\st \norm{\varf0}\leq n\}$.} \edit{To do so, we construct}{To quantify the balance between a growing Hilbert norm and improving estimate of $\op{E}$, we introduce} a secondary sequence $n_0 < n_1 < \ldots$ and constants $\vars3_{\Varf0},\vars3_{\op{E}}\geq1$ such that for each $k\in\F N$
		\begin{equation}
			n\leq n_k \implies \norm{\varf2_n} \lesssim \vars3_{\Varf0}^k, \qquad n\geq n_k \implies \op{E}_0(\varf2_n) \lesssim \vars3_{\op{E}}^{-k}.
		\end{equation}
		\edit{}{The expanding balls example would become $\spcf0^n=\{\varf0\in\F H\st \norm{\varf0}\leq \vars3_{\Varf0}^k\}$, and $\vars3_{\op{E}}$ reflects the smoothness of $\op{E}$ with respect to the Hilbert norm.} The choice of exponential scaling is \edit{very}{more} natural if we consider the $\spcf0^n$ to be the subspace of functions discretised on a uniform mesh. If that mesh is sequentially refined, then the resolution of the mesh will be of order $h^k$ after $k$ refinements and for some $h<1$. The integer $n_k$ should then be the time when the mesh has refined $k$ times. %
		\edit{The value of $\vars3_{\Varf0}$ is dictated by the smoothness of the norm of $\spcf0$ with respect to that of $\F H$. If $\norm{\varf0^*}<\infty$, then the value is $\vars3_{\Varf0}=1$, otherwise there is some damage to the rate of convergence generated by this factor. On the other hand, the value of $\vars3_{\op{E}}$ is dictated by the smoothness of $\op{E}$ at the point $\varf0^*$.}{The value $\vars3_{\Varf0}$ reflects the smoothness of the chosen basis measured in $\F H$, and $\vars3_{\op{E}}$ is a measure of efficiency with respect to the structure of $\op{E}$.} %
		If an efficient basis is used, then $\vars3_{\op{E}}$ is large. The trade-off between $\vars3_{\op{E}}$ and $\vars3_{\Varf0}$ dictates the final convergence rate of the algorithm. \edit{}{If $\vars3_{\Varf0}>1$, then we cannot guarantee the original $n^{-2}$ rate of convergence.}
	\end{adaptiveStep}

@@

	\section{L1 penalised reconstruction}\label{sec: Lasso definition}
	\edit{We now focus on the specific example of Lasso}{The canonical example for FISTA is the LASSO problem with a quadratic data fidelity and L1 regularisation. In this section we develop the necessary analytical tools for the variant with general smooth fidelity term} which will be used for numerical results in \edit{Sectoin}{Section}~\ref{sec: numerics}. We consider three forms \edit{of Lasso}{} which will be referred to as the continuous, countable, and discrete \edit{Lasso}{problem} depending on whether the space $\spcf0$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or finite dimensional respectively. In each case, the energy can be written as 
	\begin{equation}\label{eq: Lasso energy}
		\op{E}(\varf0) = \edit{\tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf0-\data)} + \mu\Norm{\varf0}
	\end{equation}
	for some $\A\colon \spcf0\to\R^m$ and $\mu>0$, where $\Norm\cdot=\norm\cdot_1$. \edit{}{We assume $\op{f}\in C^1(\R^m)$ is convex with $\nabla\op{f}$ 1-Lipschitz, and in the continuous-space case, we require $\A^*\colon\R^m\to C^1([0,1]^d)$. }Let $\varf0^*\in\argmin_{\varf0\in\spcf0}\op{E}(\varf0)$.

@@

	Application of Theorem~\ref{thm: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ although \edit{although}{} $\Norm\cdot$ is too strong a metric and results in $\vars3_{\op{E}}=2^0$. This can be seen because for any $\varf0\in L^1(\Domain)$ and Dirac mass $\delta$ supported in $(0,1)^d$, 
	\begin{equation}
		\Norm{\varf0-\delta} = \sup_{\vard0\in C(\Domain), \norm{\vard0}_{L^\infty}\leq 1} \IP{\vard0}{\varf0-\delta} = \Norm{\varf0}+\Norm{\delta} \geq 1 = \meshsize^0.
	\end{equation}
	To improve our estimate of $\vars3_{\op{E}}$ requires additional assumptions on $\A$. \edit{}{Note that the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\spcf0}^k$ onto piecewise-constant functions is $\Norm\cdot$-diminishing. Therefore }
	for any $\varf0\in\F H$, $\varf2\coloneqq \tilde{\tens{\Pi}}_k\varf0\in\tilde{\spcf0}^k$ we have
	\begin{align}
		\op{E}(\varf2)-\op{E}(\varf0) &= \edit{\tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf2-\data)-\op{f}(\A\varf0-\data)} + \mu\left(\Norm{\varf2}-\Norm{\varf0}\right)
		\\&\leq \ip{\nabla \op{f}(\A\varf2-\data)}{\A(\varf2-\varf0)}
		\\&\leq\edit{\max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0-\data}_{\ell^2})}{\left[\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2} + \norm{\A(\varf2-\varf0^*)}_{\ell^2}\right]}\norm{\A(\varf2-\varf0)}_{\ell^2}.
	\end{align}
	\edit{Choosing $\varf2 = \tilde{\tens{\Pi}}_k\varf0^*$ for any bounded linear extension to the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\spcf0\to\tilde{\spcf0}^k$ gives
	\\\centerline{$\displaystyle\op{E}(\varf2)-\op{E}(\varf0^*) \lesssim \norm{\A(\tilde{\tens{\Pi}}_k\varf0^*-\varf0^*)}_{\ell^2} \leq \norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty}\Norm{\varf0^*}.$}
	Expanding the operator norm further,
	\\\centerline{$\displaystyle
		\norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain} \frac{|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|}{\norm{\vvarx3}_{\ell^2}} \leq \sup_{\vvarx3\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}}{\norm{\vvarx3}_{\ell^2}} 
		= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}$}
	}{Clearly $\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2}$ is a constant, the second term is bounded by
	\begin{equation}
	\norm{\A(\varf2-\varf0^*)}_{\ell^2} = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{\A^*\vvarx3}{\varf2-\varf0^*} \leq \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} |\A^*\vvarx3|_{L^\infty}\Norm{\varf2-\varf0^*} \leq |\A^*|_{\ell^2\to C^0}(\Norm{\varf0}+\Norm{\varf0^*}).
	\end{equation}
	Similarly, the final term can be approximated by
	\begin{multline}
		\norm{\A(\tilde{\tens{\Pi}}_k\varf0-\varf0)}_{\ell^2}
		 = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vvarx3}{\varf0}
		\leq \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|\:\norm{\vvarx3}_{\ell^2}^{-1}\Norm{\varf0}
		\\\leq \sup_{\vvarx3\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}\: \norm{\vvarx3}_{\ell^2}^{-1} \Norm{\varf0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\varf0}
	\end{multline}}
	where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$. \edit{}{Sub-levelsets of $\op{E}$ are compact in $L^1(\Domain)$, therefore there exists a weak$^*$-converging minimising sequence $\varf0^*_j\in\F H$ such that $\varf0^*_j\rightharpoonup\varf0^*$ and $\lim_{j\to\infty}\op{E}(\varf0^*_j)=\op{E}(\varf0^*)$. 
		Combining these estimates gives 
		\begin{equation}
			\inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0^*) = \lim_{j\to\infty} \inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0_j^*) \leq \lim_{j\to\infty} \op{E}(\tilde{\tens{\Pi}}_k\varf0_j^*)-\op{E}(\varf0_j^*) \lesssim 2^{-k}.
		\end{equation}}

@@

	Heuristically, we will use strong convexity of $\op{E}^*$ and smoothness of $\A^*$ to quantify the statement:
	$$ \text{if}\quad \op{E}(\varf0_n) + \op{E}^*(\vars2_0 \vvard0_n) \approx 0 \quad \text{then}\quad \left\{\vvarx0\st \mu - |[\A^*\vvard0_n](\vvarx0)|\ll 1\right\} \subset\{\vvarx0 \st \varf0^*(\vvarx0)=0\}.$$
	\edit{First we use the strong convexity of $\op{E}^*$}{Recall that $\nabla\op{f}$ is 1-Lipschitz if and only if $\op{f}^*$ is 1-strongly convex \cite[Chapter 10, Thm. 4.2.2]{Hiriart2013}. Therefore}, if $\vars2_0\vvard0_n$ and $\vvard0^*$ are both dual-feasible, then
	\begin{equation}
		\tfrac12\norm{\vars2_0\vvard0_n-\vvard0^*}_{\ell^2}^2 \leq \op{E}^*(\vars2_0\vvard0_n) - \op{E}^*(\vvard0^*) = \op{E}^*(\vars2_0\vvard0_n) + \op{E}(\varf0^*) \leq \op{E}^*(\vars2_0\vvard0_n) + \op{E}(\varf0_n),
	\end{equation}
	which gives an easily computable bound on $\norm{\vars2_0\vvard0_n-\vvard0^*}_{\ell^2}$. Now we estimate $\A^*\vvard0_n$ on the support of $\varf0^*$:
	\begin{align}
		\min_{\vvarx0\in\supp(\varf0^*)} |[\tens{\Pi}_n\A^*\vvard0_n](\vvarx0)| &\geq \min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vvard0_n](\vvarx0)|
		\\&= \vars2_0^{-1}\min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vars2_0 \vvard0_n](\vvarx0)|
		\\&\geq \vars2_0^{-1}\min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vvard0^*](\vvarx0)| - |[\A^*\vars2_0 \vvard0_n-\A^*\vvard0^*](\vvarx0)|
		\\&= \vars2_0^{-1}\min_{\vvarx0\in\supp(\varf0^*)} \mu - |[\A^*\vars2_0 \vvard0_n-\A^*\vvard0^*](\vvarx0)|
		\\&\geq \vars2_0^{-1}\left(\mu - |\A^*|_{\ell^2\to L^\infty}\norm{\vars2_0 \vvard0_n-\vvard0^*}_{\ell^2}\right).
	\end{align}
	Therefore,
	\begin{equation}
		|[\tens{\Pi}_n\A^*\vars2_0\vvard0_n](\vvarx0)|< \mu - \sqrt{2(\op{E}(\varf0_n)+\op{E}^*(\vars2_0\vvard0_n))}|\A^*|_{\ell^2\to L^\infty} \qquad \implies \qquad \varf0^*(\vvarx0)= 0.\label{eq: support equation}
	\end{equation}
	This equation is valid when $\vvarx0$ is either a continuous or countable index, the only distinction is to switch to $\ell^\infty$ in the norm of $\A^*$. To make the equivalent statement on the discretised problem, simply replace $\vars2_0$ with $\vars2$ and $\A^*$ with $\tens{\Pi}_n\A^*$. There are two short observations on this formula:
	\begin{itemize}
		\item The convergence guarantee from Theorem~\ref{thm: exponential FISTA convergence} is for the quantity $\op{E}(\varf0_n)-\op{E}(\varf0^*)$, the more relevant quantity here is $\op{E}^*(\vars2_0\vvard0_n)+\op{E}(\varf0^*)$ for which there is no proven rate of convergence.
		\item In Section~\ref{sec: continuous lasso rate}, $|\A^*|_{\ell^2\to C^1}<\infty$ was required to compute a rate of convergence for $\op{E}(\varf0_n)$, but only $|\A^*|_{\ell^2\to L^\infty}<\infty$ is needed to estimate the support.
	\end{itemize}

@@

	\subsection{1D continuous LASSO}\label{sec: 1D Lasso examples}
	In this example we choose $\spcf0=\C M([0,1])$\edit{}{, $\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$} and $\A\colon \spcf0\to \R^{30}$ with either random Fourier kernels:
	\begin{equation}
		(\A\varf0)_j = \int_0^1\cos(\vars3_j\varx0)\varf0(\varx0), \qquad \vars3_j\sim \op{Uniform}[-100,100],\ j=1,2,\ldots,30,\ \mu =0.02, 
	\end{equation}
	or Gaussian kernels on a regular grid:
	\begin{equation}
		(\A\varf0)_j = (2\pi\sigma^2)^{-\frac12}\int_0^1\exp\left(-\frac{(\varx0-(j-1)\Delta)^2}{2\sigma^2}\right)\varf0(\varx0), \quad \sigma=0.12,\ \Delta = \tfrac1{29},\ j=1,2,\ldots,30,\ \mu=0.06.
	\end{equation}

	Several variants of FISTA are compared for these examples but the key alternative shown here is the CBP discretisation.\edit{There are many methods designed to minimise the continuous LASSO energy in \eqref{eq: Lasso energy}}{For this choice of $\op{f}$, we call \eqref{eq: Lasso energy} the continuous LASSO problem, for which there are many numerical methods} (c.f. \cite{Bredies2013,Castro2016,Boyd2017,Catala2019}) however, most \edit{}{require} the solution of a non-convex problem. We have focused on CBP because it approximates $\varf0^*$ through a convex discrete optimisation problem which is asymptotically exact in the limit $\meshsize\to0$. It can also be optimised with FISTA which allows for direct comparison with the uniform and adaptive mesh approaches. The idea is that for a fixed mesh, the kernels of $\A$ are expanded to first order on each pixel and a particular first order basis is also chosen \cite{Ekanadham2011,Duval2017b}. If $\varf0^*$ has only one Dirac spike in each pixel, then the zeroth order information should correspond to the mass of the spike and additional first order information should determine the location.

@@

	\begin{figure}\centering
		\includegraphics[width=.84\textwidth]{lasso_ndofs_convergence}
		\caption{Rates of continuous/discrete gap convergence for different LASSO algorithms with 128, 256, or 512 pixels. The `adaptive' method uses the proposed algorithm. Both `fixed' and `CBP' use standard FISTA with a uniform discretisation.}\label{fig: convergence with ndofs}
